\documentclass{acmtog}

\usepackage{amssymb,amsmath}

\acmVolume{VV}
\acmNumber{N}
\acmYear{YYYY}
\acmMonth{Month}
\acmArticleNum{XXX}
\acmdoi{10.1145/XXXXXXX.YYYYYYY}

\acmVolume{28}
\acmNumber{4}
\acmYear{2009}
\acmMonth{August}
\acmArticleNum{106}
\acmdoi{10.1145/1559755.1559763}

\begin{document}

\markboth{J. Tompson et al.}{Some Fancy Title}

\title{Some Fancy Title} % title

\author{Jonathan Tompson {\upshape and} Murphy Stein \affil{New York University}}

\category{I.3.7}{Computer Graphics}{Three-Dimensional Graphics and Realism}[Animation]
\category{I.3.5}{Computer Graphics}{Computational Geometry and Object Modeling}[Physically based modeling]

\terms{Experimentation, Human Factors}

\keywords{Hand Tracking, Neural Networks, etc}

\acmformat{Tompson, J. R. T, Stein, M. 2013. Some Fancy Title.  {ACM Trans. Graph.}}

\maketitle

\begin{bottomstuff}
Grant or Fellowship information here..
Authors' addresses: land and/or email addresses.
\end{bottomstuff}


\begin{abstract}
  Abstract Here
\end{abstract}

\section{Introduction}
\label{sec:introduction}

Introduction Here.

\section{Related Work}
\label{sec:relatedwork}

Related Work Here.

\section{Randomized Decision Forest Classifier}
\label{sec:randomizeddecisionforestclassifier}

Randomized Decision Forest Classifier Here.

\begin{equation}
\textstyle
f\left(I, u, v\right)=\left[d_I\left(u + \frac{\Delta u}{d_I\left(u,v\right)}, v + \frac{\Delta v}{d_I\left(u,v\right)}\right) - d_I\left(u,v\right)\right]\geq d_{t}
\end{equation}

\section{Dataset Creation}
\label{sec:datasetcreation}

Dataset Creation Here.

\begin{equation}
F\left(I, C\right)=k\sum_{s=1}^3\bigg(\Delta(I_s, C)\bigg) + \Phi\left(C\right) + I\left(C\right)
\end{equation}

Another one:

\begin{equation}
\Delta\left(I_s,C\right)=\sum_{u,v}\left[\operatorname{min}\left(\left|d_{I_s}(u,v)-d_{S_s}(C,u,v)\right|,d_{max}\right)\right]
\end{equation}

Another one:

\begin{equation}
\textstyle
\Phi\left(C\right) = \sum\limits_{k=1}^n\left[\operatorname{max}\left(C_k-C_{kU}, 0\right) + \operatorname{max}\left(-\left(C_{kL}-C_k\right), 0\right)\right]
\end{equation}

Another one:

\begin{equation}
f(s, t, r) = \sum_{c=1}^n\left(\frac{w_c}{n} \left\|M_s M_t M_r q_c - d_c\right\|^2 \right)
\end{equation}

Another one:

$\mathbb{R}^3$

Another one:

\begin{equation}
w_c = \frac{\operatorname{max}\left(0, \frac{n_{q_c}\cdot n_{d_c} - k}{ 1 - k}\right)}{1 + \left\|d_c-q_c\right\|}
\end{equation}

\section{Feature Detection}
\label{sec:realtimefeaturedetection}

\begin{eqnarray}
\gamma_i = \operatorname{max}\left(\gamma_{min},\gamma_0-k\left(i-1\right)\right) \\
\Delta_i = \gamma_i\Delta_{i-1}-\lambda\left(\eta w_i-\frac{\partial L}{\partial w_i}\right) \\
w_{i+1} = w_i + \Delta_i
\end{eqnarray}

\section{Pose Detection}
\label{sec:realtimeposedetection}

\begin{eqnarray}
\textstyle
\Delta_{f}\left(m\right) = \left\{
    \begin{array}{l l}
      \left\|\ \left(u_f^t, v_f^t, d_f^t\right) - \left(u_f^m, v_f^m, d_f^m\right) \right\|_2 & \text{If $d_f^t \neq 0$} \\
      \left\|\ \left(u_f^t, v_f^t\right) - \left(u_f^m, v_f^m\right) \right\|_2 & \text{otherwise}
    \end{array} \right.\ \\
f\left(m\right) = \sum\limits_{f=1}^n\left[ \Delta_{f}\left(m\right) \right] + \Phi\left(C\right) \text{   }
\end{eqnarray}

\section{Results}
\label{sec:results}

Results Here.

\section{Conclusion}
\label{sec:conclusion}

Conclusion Here.

\appendix

\section{Interesting Stuff}

Interesting Stuff Here.

\begin{acks}

Acknowledgements here.

\end{acks}

\bibliographystyle{acmtog}
\bibliography{TOG-Sample}

\received{July 2013}{July 2013}

\end{document}
