\documentclass{acmtog}

\acmVolume{VV}
\acmNumber{N}
\acmYear{YYYY}
\acmMonth{Month}
\acmArticleNum{XXX}  
\acmdoi{10.1145/XXXXXXX.YYYYYYY}

\acmVolume{28}
\acmNumber{4}
\acmYear{2009}
\acmMonth{August}
\acmArticleNum{106}  
\acmdoi{10.1145/1559755.1559763}

\begin{document}

\markboth{J. Tompson et al.}{Some Fancy Title}

\title{Some Fancy Title} % title

\author{Jonathan Tompson {\upshape and} Murphy Stein
\affil{New York University}}

\category{I.3.7}{Computer Graphics}{Three-Dimensional Graphics and Realism}[Animation]
\category{I.3.5}{Computer Graphics}{Computational Geometry and Object Modeling}[Physically based modeling]

\terms{Experimentation, Human Factors}

\keywords{Hand Tracking, Neural Networks, etc}

\acmformat{Tompson, J. R. T, Stein, M. 2013. Some Fancy Title.  {ACM Trans. Graph.}}

\maketitle

\begin{bottomstuff} 
Grant or Fellowship information here..
Authors' addresses: land and/or email addresses.
\end{bottomstuff}


\begin{abstract} 
  Abstract Here
\end{abstract}

\section{Introduction}
\label{sec:introduction}

Introduction Here.

\section{Related Work}
\label{sec:relatedwork}

Related Work Here.

\section{Randomized Decision Forest Classifier}
\label{sec:randomizeddecisionforestclassifier}

Randomized Decision Forest Classifier Here.

\begin{equation}
f\left(I, u, v\right)=\left[d_I\left(u + \frac{u_{off}}{d_I\left(u,v\right)}, v + \frac{v_{off}}{d_I\left(u,v\right)}\right) - d_I\left(u,v\right)\right]\geq d_{t}
\end{equation}

\section{Dataset Creation}
\label{sec:datasetcreation}

Dataset Creation Here.

\begin{equation}
F\left(I, C\right)=k\sum_{s=1}^3\bigg(\Delta(I_s, C)\bigg) + \Phi\left(C\right) + I\left(C\right)
\end{equation}

\begin{equation}
\Delta\left(I_s,C\right)=\sum_{u,v}\left[\operatorname{min}\left(\left|d_I_s(u,v)-d_S_s(C,u,v)\right|,d_{max}\right)\right]
\end{equation}

\begin{equation}
\Phi\left(C\right) = \sum_{k=1}^n\left[max\left(C_k-C_{k,max}, 0\right) + max\left(-\left(C_{k,min}-C_k\right), 0\right)\right]
\end{equation}

\section{Feature Detection}
\label{sec:realtimefeaturedetection}

Feature Detection Here.

\section{Pose Detection}
\label{sec:realtimeposedetection}

Pose Detection Here.

\section{Results}
\label{sec:results}

Results Here.

\section{Conclusion}
\label{sec:conclusion}

Conclusion Here.

\appendix

\section{Interesting Stuff}

Interesting Stuff Here.

\begin{acks}

Acknowledgements here.

\end{acks}

\bibliographystyle{acmtog}
\bibliography{TOG-Sample}

\received{July 2013}{July 2013}

\end{document}
